\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2016-01-22 migrating.tex
Revert a few small changes to the MigratingTable section.
See the added comments.

Live Table Migration (MigratingTable) is a library designed to transparently migrate a key-value data set between two Microsoft Azure tables~\cite{azure-table} (called the \emph{old} table and the \emph{new} table, or collectively the \emph{backend} tables) while an application is accessing this data set. The MigratingTable testing effort differs from the vNext effort in two significant ways: the \psharp test harness was developed along with the system rather than later; and it checks complete compliance with an interface specification rather than just a single liveness property. Indeed, the \psharp systematic testing engine caught bugs throughout the development process (see \S\ref{sec:eval}).

During migration, each application creates its own instance of MigratingTable (MT) that refers to the same backend tables (BTs). The application performs all data access via the MT, which provides an interface named \texttt{IChainTable} similar to that of an Azure table (the MT assumes that the BTs provide the same interface via an adapter). A \emph{migrator} job moves the data in the background. In the meantime, each \emph{logical} read and write operation issued to an MT is implemented via a sequence of \emph{backend} operations on the BTs according to a custom protocol. The protocol is designed to guarantee that the output of the logical operations complies with the \texttt{IChainTable} specification, as if all the operations were performed on a single \emph{virtual table} (VT). The goal of using \psharp was to systematically test this property.

>>>>

Live Table Migration (MigratingTable) is a library designed to transparently migrate a key-value data set between two Microsoft Azure tables~\cite{azure-table} (called the \emph{old} table and the \emph{new} table, or collectively the \emph{backend} tables) while an application is accessing this data set. The MigratingTable testing effort differs from the vNext effort in two significant ways: the \psharp test harness was developed along with the system rather than later; and it checks complete compliance with an interface specification rather than just a single liveness property. Indeed, the \psharp test caught bugs throughout the development process (see \S\ref{sec:eval}).
% In this context, saying ``the \psharp systematic testing engine caught bugs''
% sounded to me like it caught them by itself without a test harness.  In other
% contexts, this wording may not be confusing. ~ Matt 2016-01-22

% The first paragraph says the data set belongs to one application
% The way I'm describing this, the data set belongs to one (logical)
% application, which may consist of multiple processes (e.g., replicas of a web
% service).  If we wanted to talk about multiple applications sharing a data
% set, we'd need to introduce that earlier. ~ Matt 2016-01-22
%
% I want ``MT'' to refer to an instance.  With ``instance of MigratingTable
% (MT)'', it's ambiguous whether MT refers to the instance or the library.
% ~ Matt 2016-01-22
During migration, each application process creates its own MigratingTable instance (MT) that refers to the same backend tables (BTs). The application performs all data access via the MT, which provides an interface named \texttt{IChainTable} similar to that of an Azure table (the MT assumes that the BTs provide the same interface via an adapter). A \emph{migrator} job moves the data in the background. In the meantime, each \emph{logical} read and write operation issued to an MT is implemented via a sequence of \emph{backend} operations on the BTs according to a custom protocol. The protocol is designed to guarantee that the output of the logical operations complies with the \texttt{IChainTable} specification, as if all the operations were performed on a single \emph{virtual table} (VT). The goal of using \psharp was to systematically test this property.
